### 2021-06-18 paper/model/matching.tex
Apply suggestions from code review
Update Readme and add pdf.
Update templates, fix errors, copy pdf to root.
No obvious stuff left, at least nothing obvious at this time of the night.
Update matching, remove pseudocode.

The empirical data described above only allows to estimate the number of contacts each
person has. In order to simulate transmissions of Covid-19, the numbers of contacts has
to be translated into actual meetings between people. This is achieved by our matching
algorithm:

@@

Recurrent contacts are described by two components: 1) A variable in the background
characteristics. An example would be a school class identifier which could come from
actual data or be drawn randomly to achieve representative class sizes.
2) A deterministic or random function that takes the value 0 (non-participating) and 1
(participating) and can depend on the weekday, date and health state. This can be used
to model vacations, weekends or symptomatic people who stay home (see section
\ref{sec:endogenous_contact_reductions} for details).

The matching process for recurrent contacts is then extremely simple: On each simulated
day, every person who does not stay home meets all other group members who do not stay
home. The assumption that all group members have contacts with all other group members
is not fully realistic, but seems like a good approximation to reality, especially in
light of the suspected role of aerosol transmission for Covid-19 \citep{Morawska2020,
Anderson2020}.

@@

Below, we first show pseudo code for the non-recurrent matching algorithm and then
describe how the algorithm works in words.

\begin{listing}
    \label{code:matching}
    \begin{minted}{python}
        while are_unmatched_contacts_left:

            contact_type, i = draw_contact_type_and_individual()

            for _ in remaining_contacts[i, contact_type]:

                group_j = draw_group_of_other_person()
                j = draw_other_person_from_that_group(group_j)

                if infection_takes_pinfectedlaces(i, j):
                    update_health_state_of_freshly_infected()

                remaining_contacts[i, contact_type] -= 1
                remaining_contacts[j, contact_type] -= 1
    \end{minted}
    \caption{Pseudo-code of the matching algorithm for non-recurrent contacts.}
\end{listing}

We first randomly draw a contact type and individual. For each contact of the drawn
contact type that person has, we first draw the group of the other person (first stage).
Next, we calculate the probability to be drawn for each member of the group, based on
the number of remaining contacts, i.e. people who have more remaining contacts are drawn
with a higher probability. This has to be re-calculated each time because with each
matched contact, the number of remaining contacts changes. We then draw the other
individual, determine whether an infection takes place and if so update the health
state of the newly infected person. Finally, we reduce the number of remaining contacts
of the two matched individuals by one.

The recalculation of matching probabilities in the second stage is computationally
intensive because it requires summing up all remaining contacts in that group. Using a
two stage sampling process where the first stage probabilities remain constant over time
makes the matching computationally much more tractable because the number of
computations increases quadratically in the second stage group size.

>>>>

The empirical data described above only allows to estimate the number of contacts each
person has. In order to simulate transmissions of Covid-19, the numbers of contacts has
to be translated into actual meetings between people. This is achieved by a matching
algorithm:

@@

Recurrent contacts are described by two components: 1) A set of time invariant groups, such as school classes. The groups can be sampled from empirical data or created by
randomly matching simulated individuals into groups. 2) A deterministic or random function that takes the value 0 (non-participating) and 1
(participating) and can depend on the weekday, date and health state. This can be used
to model vacations, weekends or symptomatic people who stay home (see section
\ref{sec:endogenous_contact_reductions} for details).

The matching process for recurrent contacts is then extremely simple: On each simulated
day, every person who does not stay home meets all other group members who do not stay
home. The assumption that all group members have contacts with all other group members
is not fully realistic, but a good approximation to reality, especially in
light of the suspected role of aerosol transmission for Covid-19 \citep{Morawska2020,
Anderson2020}. Alternatively, the infection probability of recurrent contact types can
be interpreted as being the product of a true infection probability and the probability
that an actual contact takes place.

@@

The algorithm works as follows: First we randomly draw a contact type and individual.
For each contact of the drawn contact type that person has, we first draw the group of
the other person (first stage).
Next, we calculate the probability to be drawn for each member of the group, based on
the number of remaining contacts, i.e. people who have more remaining contacts are drawn
with a higher probability. The probabilities have to be re-calculated each time because
with each
matched contact, the number of remaining contacts changes. We then draw the other
individual, determine whether an infection takes place and if so update the health state
of the newly infected person. Finally, we reduce the number of remaining contacts of the
two matched individuals by one.\comment[id=J]{Add formulae here.}

The recalculation of matching probabilities in the second stage is computationally
intensive because it requires summing up all remaining contacts in that group. Using a
two stage sampling process where the first stage probabilities remain constant over time
makes the matching computationally much more tractable because the number of
computations only increases quadratically in the size of the second group and not
quadratically in the size of the entire simulated population.
